Index measures for oak decline severity using phenotypic descriptors

### 2019-12-11 manuscript/manuscript.Rmd
pdi package now used

$a$ = average active bleed size (cm), $A$ = number of active bleeds, $b$ = average black stain size (cm), $B$ = black stain number, $d$ = diameter at breast height (cm)

>>>>

$a$ = average active bleed size (mm), $A$ = number of active bleeds, $b$ = average black stain size (mm), $B$ = black stain number, $d$ = diameter at breast height (mm)
